LAGOS lake depth

### 2021-08-10 figures/00_maps.Rmd
linting

```{r 00_map, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
dt            <- st_read("../data/gis.gpkg", "dt", quiet = TRUE)
max_depth <- dt$lake_maxdepth_m
dt <- dt %>%
  mutate(lake_maxdepth_m = round(lake_maxdepth_m, 2)) %>%
  mutate(maxdepth_class =
    smart_cut(lake_maxdepth_m, c(10, 30, 70, 200, max(max_depth)),
      brackets = NULL, sep = " - ")
  ) %>% # unique(dt$maxdepth_class)
  dplyr::filter(!is.na(maxdepth_class))
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
states_focal  <- st_read("../data/gis.gpkg", "states_focal", quiet = TRUE)
# hu4_focal     <- st_read("../data/gis.gpkg", "hu4s_focal_simple", quiet = TRUE)
# hu4_focal     <- st_crop(st_transform(
#   lwgeom::st_make_valid(hu4_focal), st_crs(study_bbox)),
#   study_bbox)

@@

```{r gg_colocated, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
is_colocated <- read.csv("../data/lagosus_depth.csv", stringsAsFactors = FALSE) %>%
  dplyr::filter(
    lagos_effort %in% c("LAGOSNE", "bathymetry", "manual") &
      !is.na(lake_maxdepth_m) &
      !(lagoslakeid %in% c(456169))) %>% # remove llids with duplicate manual depth)
  dplyr::select(lagoslakeid, lake_state, lagos_effort, lake_maxdepth_m) %>%
  tidyr::pivot_wider(names_from = lagos_effort,
    values_from = c(lake_maxdepth_m)) %>%
  dplyr::filter(!is.na(bathymetry)) %>%
  mutate(combined = coalesce(manual, LAGOSNE)) %>%
  dplyr::filter(!is.na(combined)) %>%
  dplyr::filter(!is.na(bathymetry) & !is.na(combined)) %>%
  pull(lagoslakeid)

>>>>

```{r 00_map, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
dt            <- st_read("../data/gis.gpkg", "dt", quiet = TRUE)
max_depth <- dt$lake_maxdepth_m
dt <- dt %>%
  mutate(lake_maxdepth_m = round(lake_maxdepth_m, 2)) %>%
  mutate(maxdepth_class =
    smart_cut(lake_maxdepth_m, c(10, 30, 70, 200, max(max_depth)),
      brackets = NULL, sep = " - ")
  ) %>% # unique(dt$maxdepth_class)
  dplyr::filter(!is.na(maxdepth_class))
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
states_focal  <- st_read("../data/gis.gpkg", "states_focal", quiet = TRUE)
# hu4_focal     <- st_read("../data/gis.gpkg", "hu4s_focal_simple",
#   quiet = TRUE)
# hu4_focal     <- st_crop(st_transform(
#   lwgeom::st_make_valid(hu4_focal), st_crs(study_bbox)),
#   study_bbox)

@@

```{r gg_colocated, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
is_colocated <- read.csv("../data/lagosus_depth.csv",
  stringsAsFactors = FALSE) %>%
  dplyr::filter(
    lagos_effort %in% c("LAGOSNE", "bathymetry", "manual") &
      !is.na(lake_maxdepth_m) &
      # remove llids with duplicate manual depth)
      !(lagoslakeid %in% c(456169))) %>%
  dplyr::select(lagoslakeid, lake_state, lagos_effort, lake_maxdepth_m) %>%
  tidyr::pivot_wider(names_from = lagos_effort,
    values_from = c(lake_maxdepth_m)) %>%
  dplyr::filter(!is.na(bathymetry)) %>%
  mutate(combined = coalesce(manual, LAGOSNE)) %>%
  dplyr::filter(!is.na(combined)) %>%
  dplyr::filter(!is.na(bathymetry) & !is.na(combined)) %>%
  pull(lagoslakeid)
